A generalized definition of multidimensional item response theory parameters

### 2024-07-24 output/paper_draft/paper_M2PLM_parameters.Rmd
Corrects derivation of coordinates

In an orthogonal basis it is easy to compute the coordinates,
as they are simply the orthogonal projections onto the corresponding axis.
In the oblique case it is not so simple though, but we can take advantage of the
orthornormalization introduced above.
In basis $`r TEST_SPACE_STD_BASIS`$, the origin and end coordinates are
$`r ORIGIN_ITEM_ORTH`$ and $`r END_ITEM_ORTH`$, respectively,
and they correspond to the coordinates in $`r TEST_SPACE_BASIS`$ transformed
according to Equation \@ref(eq:discr-vector-std),
i.e., $`r ORIGIN_TRANSF_EQ`$ and $`r END_TRANSF_EQ`$.
Given the mapping of $`r TEST_SPACE_STD_BASIS`$ onto $`r LS_ORTH_BASIS`$,
the direction cosines in $`r TEST_SPACE_STD_BASIS`$
are $`r DIR_COS_ITEM_VEC_STD`$.
Therefore,

\begin{align}
  `r ORIGIN_ORTH_EQ` \\
  `r END_ORTH_EQ`.
\end{align}

Applying Proposition 2, we have that

@@

Equations \@ref(eq:origin-coords-result) and \@ref(eq:end-coords-result)
express the items coordinates in terms of their multidimensional parameters.
However, it is worth noting that the latent space Gram matrix
also plays a role in computing these coordinates,
and will therefore have an effect on the representation.
Of course,
from Equations \@ref(eq:origin-orth-discr) and \@ref(eq:end-coords-result)
it is easy to express the coordinates in terms of the parameters in the original
model formulation, namely,

>>>>

In an orthogonal basis it is easy to compute the coordinates,
as they are simply the orthogonal projections onto the corresponding axis.
In the oblique case it is not so simple though, but we can take advantage of the
orthornormalization introduced above.
In basis $`r TEST_SPACE_STD_BASIS`$, the origin and end coordinates are
$`r ORIGIN_ORTH_EQ`$ and $`r END_ORTH_EQ`$, respectively,
and they correspond to the coordinates in $`r TEST_SPACE_BASIS`$ transformed
according to Equation \@ref(eq:discr-vector-std),
i.e., $`r ORIGIN_TRANSF_EQ`$ and $`r END_TRANSF_EQ`$.
Applying Proposition 2 in the test space, we have that

@@

Equations \@ref(eq:origin-coords-result) and \@ref(eq:end-coords-result)
express the items coordinates in terms of their multidimensional parameters.
However, it is worth noting that the latent space Gram matrix
also plays a role in computing these coordinates,
and will therefore have an effect on the representation.
Of course,
from Equations \@ref(eq:origin-coords-result) and \@ref(eq:end-coords-result)
it is easy to express the coordinates in terms of the parameters in the original
model formulation, namely,
